---
title: "data_analysis_IWBD"
output: html_document
date: "2024-08-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Improve Well Being With Data Analytics

**Load relevant dependencies**

```{r}
# Load libraries
library(dplyr)
library(readxl)
library(lubridate)
library(lmerTest)
library(tidyr)    # For data reshaping
library(ggplot2)  # For creating plots
library(RColorBrewer) # For color palettes
library(ggcorrplot) # For creating correlation plots
library(wesanderson) # For color palettes
library(plm) # For panel data analysis
library(broom) # For extracting coefficients from models
library(car)
library(scales)
library(patchwork)
library(cowplot)
```

## Compare relational attachment and trusting beliefs competence

**Load data**

```{r}
# Hier deinen Pfad zur Excel-Datei einfügen
excel_path = "/Users/max/Desktop/IWB data all 2024.xlsx"
data = read_excel(excel_path, sheet = "Data_scale_values", na = c("", " "))
```

**Data cleaning**

```{r}
# convert ID to factor
data$ID = as.factor(data$ID)

data$STARTED = as.POSIXct(data$STARTED) # POSIXct: contains date and time info

data$DATE = as.Date(data$DATE)
```

**Get relevant column data**

```{r}
# Hier deine ID einfügen
id = "b6qf9a7z"

# Define start and end dates
start_date <- as.Date("2024-06-03")
end_date <- as.Date("2024-06-17")

# Create logical vector indicating whether entry is within activity interval, 0 = no, 1 = yes
data$between <- ifelse(data$DATE >= start_date & data$DATE <= end_date, 1, 0)

data_me <- data %>%
  filter(between == 1,
         QUESTNNR == "ChatGPT_Survey",
         ID == id)

data_others <- data %>%
  filter(between == 1,
         QUESTNNR == "ChatGPT_Survey",
         ID != id)

Trusting_Beliefs_Integrity_me <- data_me %>%
  select(AM_Trusting_Beliefs_Integrity) %>%
  mutate(AM_Trusting_Beliefs_Integrity = as.numeric(AM_Trusting_Beliefs_Integrity)) %>% 
   count(AM_Trusting_Beliefs_Integrity)

Trusting_Beliefs_Integrity_other <- data_others %>%
  select(AM_Trusting_Beliefs_Integrity) %>%
  mutate(AM_Trusting_Beliefs_Integrity = as.numeric(AM_Trusting_Beliefs_Integrity)) %>% 
   count(AM_Trusting_Beliefs_Integrity)

Relational_Attachment_me <- data_me %>%
  select(AM_Relational_Attachment) %>%
  mutate(AM_Relational_Attachment = as.numeric(AM_Relational_Attachment)) %>% 
  count(AM_Relational_Attachment)

Relational_Attachment_other <- data_others %>%
  select(AM_Relational_Attachment) %>%
  mutate(AM_Relational_Attachment = as.numeric(AM_Relational_Attachment)) %>% 
  count(AM_Relational_Attachment)

Familiarity_me <- data_me %>%
  select(AM_Familiarity) %>%
  mutate(AM_Familiarity = as.numeric(AM_Familiarity)) %>% 
  count(AM_Familiarity)

Familiarity_other <- data_others %>%
  select(AM_Familiarity) %>%
  mutate(AM_Familiarity = as.numeric(AM_Familiarity)) %>% 
  count(AM_Familiarity)

Trusting_Beliefs_Integrity_me$Group <- "Me"
Trusting_Beliefs_Integrity_other$Group <- "Others"
Relational_Attachment_me$Group <- "Me"
Relational_Attachment_other$Group <- "Others"
Familiarity_me$Group <- "Me"
Familiarity_other$Group <- "Others"

combined_data <- bind_rows(Trusting_Beliefs_Integrity_me, Trusting_Beliefs_Integrity_other, Relational_Attachment_me, Relational_Attachment_other, Familiarity_me, Familiarity_other)

old_daily <- c('AM_Trusting_Beliefs_Integrity', 'AM_Relational_Attachment', 'AM_Familiarity')
new <- c('Trusting_Beliefs_Integrity', 'Relational_Attachment', 'Familiarity')

combined_data <- combined_data %>% rename_with(~ new, all_of(old_daily))

combined_data_long <- combined_data %>%
  pivot_longer(cols = c(Trusting_Beliefs_Integrity, Relational_Attachment, Familiarity),
               names_to = "variable",
               values_to = "value")

combined_data_long <- combined_data_long %>%
  filter(!is.na(value))

combined_data_long$Group <- factor(combined_data_long$Group, levels = c("Me", "Others"))
```

**Plot the data**

```{r}
selected_colors <- wes_palette("Darjeeling2")[c(2,1)]

line_colors <- wes_palette("Darjeeling2")[c(2,3)]

activity_yes_no_plot <- ggplot(combined_data_long, aes(x = value)) +
  geom_bar(aes(y = n, fill = Group, alpha = Group), stat = "identity", position = "identity", width = 0.5) +
  geom_density(aes(y = ..count.., color = Group), adjust = 1) +
  facet_wrap(~ variable, scales = "free_x", switch = "x", ncol = 3) +
  labs(x = "Value", y = "Count") +
  theme_minimal() +
  theme(strip.placement = "outside",
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8),
        axis.title.y = element_text(size = 9, face = "bold"),
        axis.text.y = element_text(size = 8),
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 7),
        legend.key.size = unit(0.3,"cm"),
        legend.position = "top",
        legend.justification='left',
        legend.box = "horizontal",
        panel.background = element_rect(fill = "grey95", color = NA),
        panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white")) +
  scale_fill_manual(values = selected_colors, guide = guide_legend(byrow = TRUE, title.position = "top", title.hjust = 0)) +
  scale_color_manual(values = line_colors) +
  scale_alpha_manual(values = c("Me" = 1, "Others" = 0.6)) +
  scale_y_continuous(limits = c(0, 50), oob = scales::squish) +
  scale_x_continuous(breaks = function(x) seq(ceiling(min(x)), floor(max(x)), by = 1),
                   labels = function(x) as.integer(x))

print(activity_yes_no_plot)

ggsave("activity_yes_no_plot.pdf", activity_yes_no_plot, width = 16, height = 7, units = "cm")
```

## Regression analysis effect of ChatGPT on well-being over time

**Load data**

```{r}
# Hier deinen Pfad zur Excel-Datei einfügen
excel_path = "/Users/max/Desktop/IWB data all 2024.xlsx"
data = read_excel(excel_path, sheet = "Data_scale_values", na = c("", " "))
```

**Data cleaning**

```{r}
# convert ID to factor
data$ID = as.factor(data$ID)

data$STARTED = as.POSIXct(data$STARTED) # POSIXct: contains date and time info

data$DATE = as.Date(data$DATE)
```

**Get relevant column data**

```{r}
# Hier deine ID einfügen
id = "b6qf9a7z"

# Define start and end dates
start_date <- as.Date("2024-06-03")
end_date <- as.Date("2024-06-17")

# Create logical vector indicating whether entry is within activity interval, 0 = no, 1 = yes
data$between <- ifelse(data$DATE >= start_date & data$DATE <= end_date, 1, 0)

data_me <- data %>%
  filter(between == 1,
         QUESTNNR == "ChatGPT_Survey",
         ID == id)

data_me$Group <- "Me"

data_others <- data %>%
  filter(between == 1,
         QUESTNNR == "ChatGPT_Survey",
         ID != id)

data_others$Group <- "Others"

CB_me <- data_me %>%
  select(AM_Cognitive_Well_Being, DATE, Group) %>%
  mutate(AM_Cognitive_Well_Being = as.numeric(AM_Cognitive_Well_Being))

CB_other <- data_others %>%
  select(AM_Cognitive_Well_Being, DATE, Group) %>%
  group_by(DATE) %>% 
  mutate(AM_Cognitive_Well_Being = as.numeric(AM_Cognitive_Well_Being)) %>% summarise(AM_Cognitive_Well_Being = mean(AM_Cognitive_Well_Being, na.rm = TRUE)) %>%
  ungroup()

CB_other$Group <- "Others"

AWB_P_me <- data_me %>%
  select(AM_Affective_Well_Being_Positive, DATE, Group) %>%
  mutate(AM_Affective_Well_Being_Positive = as.numeric(AM_Affective_Well_Being_Positive))

AWB_N_me <- data_me %>%
  select(AM_Affective_Well_Being_Negative, DATE, Group) %>%
  mutate(AM_Affective_Well_Being_Negative = as.numeric(AM_Affective_Well_Being_Negative))

AWB_P_other <- data_others %>%
  select(AM_Affective_Well_Being_Positive, DATE, Group) %>%
  group_by(DATE) %>% 
  mutate(AM_Affective_Well_Being_Positive = as.numeric(AM_Affective_Well_Being_Positive)) %>% summarise(AM_Affective_Well_Being_Positive = mean(AM_Affective_Well_Being_Positive, na.rm = TRUE)) %>%
  ungroup()

AWB_P_other$Group <- "Others"

AWB_N_other <- data_others %>%
  select(AM_Affective_Well_Being_Negative, DATE, Group) %>%
   group_by(DATE) %>% 
  mutate(AM_Affective_Well_Being_Negative = as.numeric(AM_Affective_Well_Being_Negative)) %>% summarise(AM_Affective_Well_Being_Negative = mean(AM_Affective_Well_Being_Negative, na.rm = TRUE)) %>%
  ungroup()

AWB_N_other$Group <- "Others"

AA_me <- data_me %>%
  select(AM_Anger_and_Anxiety, DATE, Group) %>%
  mutate(AM_Anger_and_Anxiety = as.numeric(AM_Anger_and_Anxiety))

AA_other <- data_others %>%
  select(AM_Anger_and_Anxiety, DATE, Group) %>%
  group_by(DATE) %>% 
  mutate(AM_Anger_and_Anxiety = as.numeric(AM_Anger_and_Anxiety)) %>% summarise(AM_Anger_and_Anxiety = mean(AM_Anger_and_Anxiety, na.rm = TRUE)) %>%
  ungroup()

AA_other$Group <- "Others"

CB_comparison <- bind_rows(CB_me, CB_other)
AWB_P_comparison <- bind_rows(AWB_P_me, AWB_P_other)
AWB_N_comparison <- bind_rows(AWB_N_me, AWB_N_other)
AA_comparison <- bind_rows(AA_me, AA_other)
```

**Plot the data**

```{r}
all_colors <- wes_palette("Darjeeling2")
selected_colors <- all_colors[c(2,1)]

spreed_colors <- wes_palette("Darjeeling2")[c(1)]

custom_theme <- theme_minimal() +
  theme(panel.background = element_rect(fill = "grey95", color = NA),
        panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        axis.title.x = element_text(size = 8, face = "italic"),
       # axis.title.x = element_blank(),
        axis.title.y = element_text(size = 8, face = "bold"),
        legend.key.size = unit(0.3,"cm"),
        legend.position = "top",
        legend.justification='right',
        legend.box = "horizontal",
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 7))

guide <- guide_legend(byrow = TRUE, title.position = "top", title.hjust = 0)

# Create the SP Experiences plot
CB_plot <- ggplot(CB_comparison, aes(x = DATE, y = AM_Cognitive_Well_Being, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, aes(fill = Group), formula = y ~ x) +
  labs(y = "Score",
       x = "Cognitive Well Being",
       color = "Data Source",
       fill = "Data Source") +
  scale_color_manual(values = selected_colors) +
  scale_fill_manual(values = c("Me" = "lightblue", "Others" = spreed_colors, guide = guide)) +
  custom_theme +
  guides(color = guide, fill = guide)

AWB_P_plot <- ggplot(AWB_P_comparison, aes(x = DATE, y = AM_Affective_Well_Being_Positive, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, aes(fill = Group), formula = y ~ x) +
  labs(y = "Score",
       x = "Affective Well Being Positive",
       color = "Data Source",
       fill = "Data Source") +
  scale_color_manual(values = selected_colors) +
  scale_fill_manual(values = c("Me" = "lightblue", "Others" = spreed_colors, guide = guide)) +
  custom_theme +
  guides(color = guide, fill = guide)

AWB_N_plot <- ggplot(AWB_N_comparison, aes(x = DATE, y = AM_Affective_Well_Being_Negative, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, aes(fill = Group), formula = y ~ x) +
  labs(y = "Score",
       x = "Affective Well Being Negative",
       color = "Data Source",
       fill = "Data Source") +
  scale_color_manual(values = selected_colors) +
  scale_fill_manual(values = c("Me" = "lightblue", "Others" = spreed_colors, guide = guide)) +
  custom_theme +
  guides(color = guide, fill = guide)

AA_plot <- ggplot(AA_comparison, aes(x = DATE, y = AM_Anger_and_Anxiety, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, aes(fill = Group), formula = y ~ x) +
  labs(y = "Score",
       x = "Anger and Anxiety",
       color = "Data Source",
       fill = "Data Source") +
  scale_color_manual(values = selected_colors) +
  scale_fill_manual(values = c("Me" = "lightblue", "Others" = spreed_colors, guide = guide)) +
  custom_theme +
  guides(color = guide, fill = guide)

combined_plot <- CB_plot + AWB_P_plot + AWB_N_plot + AA_plot +
  plot_layout(ncol = 2, guides = "collect") +
  plot_annotation(
    title = "Comparison of Social Media and Social Presence Experiences",
    theme = theme(plot.title = element_blank(),
                  legend.key.size = unit(0.3,"cm"),
                  legend.justification='left',
                  legend.position = "top",
                  legend.box = "horizontal"))

print(combined_plot)

ggsave("regression_well_being_plot.pdf", combined_plot, width = 16, height = 9, units = "cm")
```

## Regression plot prompt type, RA, instrumental and emotionale support satisfaction over time

**Load data**

```{r}
# Hier deinen Pfad zur Excel-Datei einfügen
excel_path = "/Users/max/Desktop/IWB data all 2024.xlsx"
data = read_excel(excel_path, sheet = "Data_scale_values", na = c("", " "))
```

**Data cleaning**

```{r}
# convert ID to factor
data$ID = as.factor(data$ID)

data$STARTED = as.POSIXct(data$STARTED) # POSIXct: contains date and time info

data$DATE = as.Date(data$DATE)
```

**Get relevant column data**

```{r}
# Hier deine ID einfügen
id = "b6qf9a7z"

# Define start and end dates
start_date <- as.Date("2024-06-03")
end_date <- as.Date("2024-06-17")

# Create logical vector indicating whether entry is within activity interval, 0 = no, 1 = yes
data$between <- ifelse(data$DATE >= start_date & data$DATE <= end_date, 1, 0)

data_me <- data %>%
  filter(between == 1,
         QUESTNNR == "ChatGPT_Survey",
         ID == id)

data_me$Group <- "Me"

data_others <- data %>%
  filter(between == 1,
         QUESTNNR == "ChatGPT_Survey",
         ID != id)

data_others$Group <- "Others"

Relational_Attachment_me <- data_me %>%
  select(AM_Relational_Attachment, DATE, Group) %>%
  mutate(AM_Relational_Attachment = as.numeric(AM_Relational_Attachment))

Relational_Attachment_other <- data_others %>%
  select(AM_Relational_Attachment, DATE, Group) %>%
  group_by(DATE) %>% 
  mutate(AM_Relational_Attachment = as.numeric(AM_Relational_Attachment)) %>% summarise(AM_Relational_Attachment = mean(AM_Relational_Attachment, na.rm = TRUE)) %>%
  ungroup()

Relational_Attachment_other$Group <- "Others"

SIS_me <- data_me %>%
  select(AM_Satisfaction_Instrumental_Support, DATE, Group) %>%
  mutate(AM_Satisfaction_Instrumental_Support = as.numeric(AM_Satisfaction_Instrumental_Support))

SIS_other <- data_others %>%
  select(AM_Satisfaction_Instrumental_Support, DATE, Group) %>%
  group_by(DATE) %>% 
  mutate(AM_Satisfaction_Instrumental_Support = as.numeric(AM_Satisfaction_Instrumental_Support)) %>% summarise(AM_Satisfaction_Instrumental_Support = mean(AM_Satisfaction_Instrumental_Support, na.rm = TRUE)) %>%
  ungroup()

SIS_other$Group <- "Others"

SES_me <- data_me %>%
  select(AM_Satisfaction_Emotional_Support, DATE, Group) %>%
  mutate(AM_Satisfaction_Emotional_Support = as.numeric(AM_Satisfaction_Emotional_Support))

SES_other <- data_others %>%
  select(AM_Satisfaction_Emotional_Support, DATE, Group) %>%
  group_by(DATE) %>% 
  mutate(AM_Satisfaction_Emotional_Support = as.numeric(AM_Satisfaction_Emotional_Support)) %>% summarise(AM_Satisfaction_Emotional_Support = mean(AM_Satisfaction_Emotional_Support, na.rm = TRUE)) %>%
  ungroup()

SES_other$Group <- "Others"

IV_prompts_me <- data_me %>%
  select(IV, DATE, Group) %>%
  mutate(IV = as.numeric(IV))

IV_prompts_other <- data_others %>%
  select(IV, DATE, Group) %>%
  group_by(DATE) %>%
  mutate(IV = as.numeric(IV)) %>% summarise(IV = mean(IV, na.rm = TRUE)) %>%
  ungroup()

IV_prompts_other$Group <- "Others"

RA_comparison <- bind_rows(Relational_Attachment_me, Relational_Attachment_other)
SIS_comparison <- bind_rows(SIS_me, SIS_other)
SES_comparison <- bind_rows(SES_me, SES_other)
IV_prompts_comparison <- bind_rows(IV_prompts_me, IV_prompts_other)
```

**Plot the data**

```{r}
all_colors <- wes_palette("Darjeeling2")
selected_colors <- all_colors[c(2,1)]

spreed_colors <- wes_palette("Darjeeling2")[c(1)]

custom_theme <- theme_minimal() +
  theme(panel.background = element_rect(fill = "grey95", color = NA),
        panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        axis.title.x = element_text(size = 8, face = "italic"),
       # axis.title.x = element_blank(),
        axis.title.y = element_text(size = 8, face = "bold"),
        legend.key.size = unit(0.3,"cm"),
        legend.position = "top",
        legend.justification='right',
        legend.box = "horizontal",
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 7))

guide <- guide_legend(byrow = TRUE, title.position = "top", title.hjust = 0)

# Create the SM Experiences plot
RA_plot <- ggplot(RA_comparison, aes(x = DATE, y = AM_Relational_Attachment, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, aes(fill = Group), formula = y ~ x) +
  labs(y = "Score",
       x = "Relational Attachment",
       color = "Data Source",
       fill = "Data Source") +
  scale_color_manual(values = selected_colors) +
  scale_fill_manual(values = c("Me" = "lightblue", "Others" = spreed_colors, guide = guide)) +
  custom_theme +
  guides(color = guide, fill = guide)

SIS_plot <- ggplot(SIS_comparison, aes(x = DATE, y = AM_Satisfaction_Instrumental_Support, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, aes(fill = Group), formula = y ~ x) +
  labs(y = "Score",
       x = "Satisfaction Instrumental Support",
       color = "Data Source",
       fill = "Data Source") +
  scale_color_manual(values = selected_colors) +
  scale_fill_manual(values = c("Me" = "lightblue", "Others" = spreed_colors, guide = guide)) +
  custom_theme +
  guides(color = guide, fill = guide)

SES_plot <- ggplot(SES_comparison, aes(x = DATE, y = AM_Satisfaction_Emotional_Support, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, aes(fill = Group), formula = y ~ x) +
  labs(y = "Score",
       x = "Satisfaction Emotional Support",
       color = "Data Source",
       fill = "Data Source") +
  scale_color_manual(values = selected_colors) +
  scale_fill_manual(values = c("Me" = "lightblue", "Others" = spreed_colors, guide = guide)) +
  custom_theme +
  guides(color = guide, fill = guide)

IV_plot <- ggplot(IV_prompts_comparison, aes(x = DATE, y = IV, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, aes(fill = Group), formula = y ~ x) +
  labs(y = "Type of Prompt",
       x = "Prompt Selection Over Time",
       color = "Data Source",
       fill = "Data Source") +
  scale_color_manual(values = selected_colors) +
  scale_fill_manual(values = c("Me" = "lightblue", "Others" = spreed_colors, guide = guide)) +
  custom_theme +
  guides(color = guide, fill = guide)

combined_plot <- RA_plot + SIS_plot + SES_plot + IV_plot +
  plot_layout(ncol = 2, guides = "collect") +
  plot_annotation(
    title = "Comparison of Social Media and Social Presence Experiences",
    theme = theme(plot.title = element_blank(),
                  legend.key.size = unit(0.3,"cm"),
                  legend.justification='left',
                  legend.position = "top",
                  legend.box = "horizontal"))

print(combined_plot)

ggsave("regression_prompt_satisfaction_plot.pdf", combined_plot, width = 16, height = 9, units = "cm")
```

## Boxplot prompt type and satisfaction

**Load data**

```{r}
# Hier deinen Pfad zur Excel-Datei einfügen
excel_path = "/Users/max/Desktop/IWB data all 2024.xlsx"
data = read_excel(excel_path, sheet = "Data_scale_values", na = c("", " "))
```

**Data cleaning**

```{r}
# convert ID to factor
data$ID = as.factor(data$ID)

data$STARTED = as.POSIXct(data$STARTED) # POSIXct: contains date and time info

data$DATE = as.Date(data$DATE)
```

**Get relevant column data**

```{r}
# Hier deine ID einfügen
id = "b6qf9a7z"

# Define start and end dates
start_date <- as.Date("2024-06-03")
end_date <- as.Date("2024-06-17")

# Create logical vector indicating whether entry is within activity interval, 0 = no, 1 = yes
data$between <- ifelse(data$DATE >= start_date & data$DATE <= end_date, 1, 0)

data_me <- data %>%
  filter(between == 1,
         QUESTNNR == "ChatGPT_Survey",
         ID == id) %>% 
  select(IV, AM_Satisfaction_Instrumental_Support, AM_Satisfaction_Emotional_Support)


SIS_me <- data_me %>%
  select(AM_Satisfaction_Instrumental_Support, IV) %>%
  mutate(AM_Satisfaction_Instrumental_Support = as.numeric(AM_Satisfaction_Instrumental_Support),
         IV = as.numeric(IV))

SIS_me$Group <- "Instrumental_Support"

SIS_me <- SIS_me %>% 
  rename(Satisfaction = AM_Satisfaction_Instrumental_Support)

SES_me <- data_me %>%
  select(AM_Satisfaction_Emotional_Support, IV) %>%
  mutate(AM_Satisfaction_Emotional_Support = as.numeric(AM_Satisfaction_Emotional_Support),
         IV = as.numeric(IV))

SES_me$Group <- "Emotional_Support"

SES_me <- SES_me %>% 
  rename(Satisfaction = AM_Satisfaction_Emotional_Support)

combined_data <- rbind(SIS_me, SES_me)
```

**Plot the data**

```{r}
selected_colors <- brewer.pal(6, "Blues")[c(2, 3, 4, 5)]

spreed_colors <- wes_palette("Darjeeling2")[c(1)]

custom_theme <- theme_minimal() +
  theme(panel.background = element_rect(fill = "grey95", color = NA),
        panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        axis.title.x = element_text(size = 8, face = "bold"),
        #axis.title.x = element_blank(),
        axis.title.y = element_text(size = 8, face = "bold"),
        legend.key.size = unit(0.3,"cm"),
        legend.position = "top",
        legend.justification='left',
        legend.box = "horizontal",
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 7))

guide <- guide_legend(byrow = TRUE, title.position = "top", title.hjust = 0)

SES_plot <- ggplot(SES_me, aes(x = factor(IV), y = Satisfaction)) +
  geom_boxplot(aes(fill = factor(IV))) +
  labs(x = "Prompt Type", 
       y = "Emotional Satisfaction",
       fill = "Prompt Type") +
  scale_fill_manual(values = selected_colors,
                    labels = c("1" = "General", 
                                 "2" = "Emotional", 
                                 "3" = "Instrumental", 
                                 "4" = "Emotional & Instrumental")) +
  scale_x_discrete(labels = c("General", "Emotional", "Instrumental", "Emotional & Instrumental")) +
    custom_theme +
  theme(axis.title.x = element_blank()) +
  guides(color = guide, fill = guide)

SIS_plot <- ggplot(SIS_me, aes(x = factor(IV), y = Satisfaction)) +
  geom_boxplot(aes(fill = factor(IV))) +
  labs(x = "Prompt Type", 
       y = "Instrumental Satisfaction",
       fill = "Prompt Type") +
  scale_fill_manual(values = selected_colors,
                    labels = c("1" = "General", 
                                 "2" = "Emotional", 
                                 "3" = "Instrumental", 
                                 "4" = "Emotional & Instrumental")) +
  scale_x_discrete(labels = c("General", "Emotional", "Instrumental", "Emotional & Instrumental")) +
    custom_theme +
  guides(color = guide, fill = guide)


combined_plot <- SES_plot + SIS_plot +
  plot_layout(ncol = 1, guides = "collect") +
  plot_annotation(
    title = "Comparison of Social Media and Social Presence Experiences",
    theme = theme(plot.title = element_blank(),
                  legend.key.size = unit(0.3,"cm"),
                  legend.justification='left',
                  legend.position = "top",
                  legend.box = "horizontal"))

print(combined_plot)

ggsave("boxplot_prompt_satisfaction_plot.pdf", combined_plot, width = 16, height = 9.5, units = "cm")
```

