---
title: "data_analysis_IWBD"
output: html_document
date: "2024-08-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Improve Well Being With Data Analytics

## Analyse subjective data

**Load relevant dependencies**

```{r}
# Load libraries
library(dplyr)
library(readxl)
library(lubridate)
library(lmerTest)
library(tidyr)    # For data reshaping
library(ggplot2)  # For creating plots
library(RColorBrewer) # For color palettes
library(ggcorrplot) # For creating correlation plots
library(wesanderson) # For color palettes
library(plm) # For panel data analysis
library(broom) # For extracting coefficients from models
library(car)
library(scales)
library(patchwork)
```

### Plot differences in well being

**Load data**

```{r}
# Hier deinen Pfad zur Excel-Datei einfügen
excel_path = "/Users/max/Desktop/IWB data all 2024.xlsx"
data = read_excel(excel_path, sheet = "Data_scale_values", na = c("", " "))
```

**Data cleaning**

```{r}
# convert ID to factor
data$ID = as.factor(data$ID)

data$STARTED = as.POSIXct(data$STARTED) # POSIXct: contains date and time info

data$DATE = as.Date(data$DATE)
```

**Get relevant column data**

```{r}
# Hier deine ID einfügen
id = ""

new <- c('Cognitive_Well_Being', 'Affective_Well_Being_Positive', 'Affective_Well_Being_Negative')
old_daily <- c('EV_Cognitive_Well_Being', 'EV_Affective_Well_Being_Positive', 'EV_Affective_Well_Being_Negative')
old_basis <- c('BS_Cognitive_Well_Being', 'BS_Affective_Well_Being', 'BS_Affective_Well_Being_Negative')

necessary_basis_columns <- c('BS_Cognitive_Well_Being', 'BS_Affective_Well_Being', 'BS_Affective_Well_Being_Negative')
necessary_daily_columns <- c('EV_Cognitive_Well_Being', 'EV_Affective_Well_Being_Positive', 'EV_Affective_Well_Being_Negative')

basis_median <- data %>% 
  filter(QUESTNNR == "Basis_Survey") %>% 
  filter(ID != id) %>%
  select(all_of(necessary_basis_columns), -ID, -DATE, -STARTED, -IV) %>%
  mutate(across(all_of(necessary_basis_columns), as.numeric)) %>%
  summarise(across(everything(), median)) %>%
  select(where(~!is.na(.)))
  
my_basis_survey <- data %>% 
  filter(QUESTNNR == "Basis_Survey") %>% 
  filter(ID == id) %>%
  select(all_of(necessary_basis_columns), -ID, -DATE, -STARTED, -IV) %>%
  mutate(across(all_of(necessary_basis_columns), as.numeric)) %>%
  summarise(across(everything(), median)) %>%
  select(where(~!is.na(.)))

basis_daily_median <- data %>% 
  filter(QUESTNNR == "Daily_Evening_Survey") %>%
  filter(WEEK==27) %>%
  filter(EV_Activity_Check==2) %>%
  filter(ID != id) %>%
  select(all_of(necessary_daily_columns), -ID, -DATE, -STARTED, -IV) %>%
  mutate(across(all_of(necessary_daily_columns), as.numeric)) %>%
  summarise(across(everything(), median)) %>%
  select(where(~!is.na(.)))

my_basis_daily_survey <- data %>% 
  filter(QUESTNNR == "Daily_Evening_Survey") %>% 
  filter(WEEK==27) %>%
  filter(EV_Activity_Check==2) %>%
  filter(ID == id) %>% 
  select(all_of(necessary_daily_columns), -ID, -DATE, -STARTED, -IV) %>%
  mutate(across(all_of(necessary_daily_columns), as.numeric)) %>%
  select(where(~!all(is.na(.)))) %>%
  summarise(across(everything(), median))

# Select relevant columns from my_basis_daily_survey
my_basis_daily_results <- my_basis_daily_survey %>%
  select(all_of(necessary_daily_columns)) %>%
  mutate(Group = "Your Results")

# Select relevant columns from basis_daily_median
median_basis_daily_results <- basis_daily_median %>%
  select(all_of(necessary_daily_columns)) %>%
  mutate(Group = "Median Results")

my_basis_results <- my_basis_survey %>%
  select(all_of(necessary_basis_columns)) %>%
  mutate(Group = "Your Results")

median_basis_results <- basis_median %>%
  select(all_of(necessary_basis_columns)) %>%
  mutate(Group = "Median Results")

# Select relevant columns from my_basis_daily_survey
end_results_me <- my_basis_daily_survey %>%
  select(all_of(necessary_daily_columns))

end_results_me <- end_results_me %>% 
  rename_with(~ new, all_of(old_daily))

# Select relevant columns from basis_daily_median
end_results_other <- basis_daily_median %>%
  select(all_of(necessary_daily_columns))

end_results_other <- end_results_other %>% 
  rename_with(~ new, all_of(old_daily))

start_results_me <- my_basis_survey %>%
  select(BS_Cognitive_Well_Being, 
         BS_Affective_Well_Being, 
         BS_Affective_Well_Being_Negative)

start_results_me <- start_results_me %>% 
  rename_with(~ new, all_of(old_basis))

start_results_others <- basis_median %>%
  select(all_of(necessary_basis_columns))

start_results_others <- start_results_others %>% 
  rename_with(~ new, all_of(old_basis))

difference_me <- end_results_me - start_results_me
difference_others <- end_results_other - start_results_others

difference_me <- difference_me %>% 
  mutate(Group = "My Results")

difference_others <- difference_others %>%
  mutate(Group = "Other Results")

combined_results <- rbind(difference_me, difference_others)

plot_data <- combined_results %>%
  pivot_longer(cols = c(Cognitive_Well_Being, 
                        Affective_Well_Being_Positive, 
                        Affective_Well_Being_Negative),
               names_to = "Measure", 
               values_to = "Score")
```

**Plotting differences in well being**

```{r}
all_colors <- wes_palette("Darjeeling2")
selected_colors <- all_colors[c(4,1)]

differences_plot <- ggplot(plot_data, aes(x = Measure, y = Score, fill = Group)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.8) +
  geom_text(aes(label = round(Score, 2)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, color = "black", size = 2.5) +
  labs(x = "Well Being Categories", 
       y = "Difference",
       fill = "Data Source") +
  scale_x_discrete(limits = c("Cognitive_Well_Being", 
                              "Affective_Well_Being_Positive", 
                              "Affective_Well_Being_Negative"),
                   labels = c("Cognitive", "Affective Positive", "Affective Negative")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
    axis.title.x =  element_text(size = 8, face = "bold"),
    axis.title.y = element_text(size = 8, face = "bold"),
    legend.title = element_text(size = 8, face = "bold"),
    legend.key.size = unit(0.3,"cm"),
    legend.text = element_text(size = 7), 
    legend.position = "top",
    legend.justification='left',
    legend.box = "horizontal",
     panel.background = element_rect(fill = "grey95", color = NA),
    panel.grid.major = element_line(color = "white"),
    panel.grid.minor = element_line(color = "white")) +
  scale_fill_manual(values = selected_colors, guide = guide_legend(byrow = TRUE, title.position = "top", title.hjust = 0)) +
  ylim(min(plot_data$Score) * 1.2, max(plot_data$Score) * 1.2)

print(differences_plot)

ggsave("well_being_differences_plot.pdf", differences_plot, width = 16, height = 9, units = "cm")
```

------------------------------------------------------------------------

### Create correlation matrix for „C_WB_AVG“, „A_WB_P_AVG“, „A_WB_N_AVG“, „RD_AVG“, „PITU_EX“, „SP_EX“, and „SM_EX“

**Load data**

```{r}
# Hier deinen Pfad zur Excel-Datei einfügen
excel_path = ""
data = read_excel(excel_path, sheet = "Data_scale_values", na = c("", " "))
```

**Data cleaning**

```{r}
# convert ID to factor
data$ID = as.factor(data$ID)

data$STARTED = as.POSIXct(data$STARTED) # POSIXct: contains date and time info

data$DATE = as.Date(data$DATE)
```

**Get relevant column data**

```{r}
# Hier deine ID einfügen
id = ""

# Define start and end dates
start_date <- as.Date("2024-06-24")
end_date <- as.Date("2024-07-07")

# Create logical vector indicating whether entry is within activity interval, 0 = no, 1 = yes
data$between <- ifelse(data$DATE >= start_date & data$DATE <= end_date, 1, 0)

data_only_free_activity <- data %>%
  filter(between == 1) %>%
  filter(QUESTNNR != "Basis_Survey") %>%
  filter(QUESTNNR != "ChatGPT_Survey") %>% 
  filter(EV_Activity_Check == 2)

PITU_EX <- data_only_free_activity %>%
  filter(EV_Activity_Check == 2) %>%
  filter(ID == id) %>%
  select(EV_PITU_Experiences)  %>%
  rowwise() %>%
  mutate(EV_PITU_Experiences = as.numeric(EV_PITU_Experiences))

SP_EX <- data_only_free_activity %>%
  filter(EV_Activity_Check == 2) %>%
  filter(ID == id) %>%
  select(EV_SP_Experiences)  %>%
  rowwise() %>%
  mutate(EV_SP_Experiences = as.numeric(EV_SP_Experiences))

SM_EX <- data_only_free_activity %>%
  filter(EV_Activity_Check == 2) %>%
  filter(ID == id) %>%
  select(EV_SM_Experiences)  %>%
  rowwise() %>%
  mutate(EV_SM_Experiences = as.numeric(EV_SM_Experiences))

cor_data <- data_only_free_activity %>%
  filter(EV_Activity_Check==2) %>%
  filter(ID == id) %>%
  select(EV_Cognitive_Well_Being, 
         EV_Affective_Well_Being_Positive, 
         EV_Affective_Well_Being_Negative,
         EV_Resource_Depletion) %>%
  mutate(EV_Cognitive_Well_Being = as.numeric(EV_Cognitive_Well_Being),
         EV_Affective_Well_Being_Positive = as.numeric(EV_Affective_Well_Being_Positive),
         EV_Affective_Well_Being_Negative = as.numeric(EV_Affective_Well_Being_Negative),
         EV_Resource_Depletion = as.numeric(EV_Resource_Depletion))

combined_data_EX <- cbind(PITU_EX, SP_EX, SM_EX, cor_data)

old_daily <- c('EV_PITU_Experiences', 'EV_SP_Experiences', 'EV_SM_Experiences', 'EV_Cognitive_Well_Being', 'EV_Affective_Well_Being_Positive', 
               'EV_Affective_Well_Being_Negative', 'EV_Resource_Depletion')

new <- c('PITU_EX', 'SP_EX', 'SM_EX', 'C_WB_AVG', 'A_WB_P_AVG', 'A_WB_N_AVG', 'RD_AVG')

combined_data_EX <- combined_data_EX %>% rename_with(~ new, all_of(old_daily))

correlation_matrix_EX <- cor(combined_data_EX, use = "pairwise.complete.obs")
```

**Create correlation matrix**

```{r}
correlation_matrix_sat <- cor(combined_data_EX, use = "pairwise.complete.obs")
```

**Plotting correlation matrix**

```{r}
correlation_matrix_plot <- ggcorrplot(correlation_matrix_EX, 
           method ="square", 
           hc.order = TRUE,
           lab = TRUE,
           outline.color = "white", 
           ggtheme = ggplot2::theme_gray,
           colors = c("#ECCBAE", "white", "#046C9A"))


print(correlation_matrix_plot)
```

------------------------------------------------------------------------

### Compare satisfaction on IT, SP, and SM with cognitive well being

**Load data**

```{r}
# Hier deinen Pfad zur Excel-Datei einfügen
excel_path = ""
data = read_excel(excel_path, sheet = "Data_scale_values", na = c("", " "))
```

**Data cleaning**

```{r}
# convert ID to factor
data$ID = as.factor(data$ID)

data$STARTED = as.POSIXct(data$STARTED) # POSIXct: contains date and time info

data$DATE = as.Date(data$DATE)
```

**Get relevant column data**

```{r}
# Hier deine ID einfügen
id = ""

# Define start and end dates
start_date <- as.Date("2024-06-24")
end_date <- as.Date("2024-07-07")

# Create logical vector indicating whether entry is within activity interval, 0 = no, 1 = yes
data$between <- ifelse(data$DATE >= start_date & data$DATE <= end_date, 1, 0)

data_only_free_activity <- data %>%
  filter(between == 1) %>%
  filter(QUESTNNR == "Daily_Evening_Survey") %>% 
  filter(EV_Activity_Check == 2)


data_only_no_activity <- data %>%
  filter(QUESTNNR != "Basis_Survey") %>%
  filter(QUESTNNR != "ChatGPT_Survey") %>%
  filter(EV_Activity_Check == 1) 

COG_WB_free <- data_only_free_activity %>%
  filter(ID == id) %>%
  select(EV_Cognitive_Well_Being)  %>%
  rowwise() %>%
  mutate(EV_Cognitive_Well_Being = as.numeric(EV_Cognitive_Well_Being)) %>% 
  count(EV_Cognitive_Well_Being)

COG_WB_no <- data_only_no_activity %>%
  filter(ID == id) %>%
  select(EV_Cognitive_Well_Being)  %>%
  rowwise() %>%
  mutate(EV_Cognitive_Well_Being = as.numeric(EV_Cognitive_Well_Being)) %>% 
  count(EV_Cognitive_Well_Being)

AFF_WB_P_free <- data_only_free_activity %>%
  filter(ID == id) %>%
  select(EV_Affective_Well_Being_Positive)  %>%
  rowwise() %>%
  mutate(EV_Affective_Well_Being_Positive = as.numeric(EV_Affective_Well_Being_Positive)) %>% 
  count(EV_Affective_Well_Being_Positive)

AFF_WB_P_no <- data_only_no_activity %>%
  filter(ID == id) %>%
  select(EV_Affective_Well_Being_Positive)  %>%
  rowwise() %>%
  mutate(EV_Affective_Well_Being_Positive = as.numeric(EV_Affective_Well_Being_Positive)) %>% 
  count(EV_Affective_Well_Being_Positive)

AFF_WB_N_free <- data_only_free_activity %>%
  filter(ID == id) %>%
  select(EV_Affective_Well_Being_Negative)  %>%
  rowwise() %>%
  mutate(EV_Affective_Well_Being_Negative = as.numeric(EV_Affective_Well_Being_Negative)) %>% 
  count(EV_Affective_Well_Being_Negative)

AFF_WB_N_no <- data_only_no_activity %>%
  filter(ID == id) %>%
  select(EV_Affective_Well_Being_Negative)  %>%
  rowwise() %>%
  mutate(EV_Affective_Well_Being_Negative = as.numeric(EV_Affective_Well_Being_Negative)) %>% 
  count(EV_Affective_Well_Being_Negative)

RD_free <- data_only_free_activity %>%
  filter(ID == id) %>%
  select(EV_Resource_Depletion)  %>%
  rowwise() %>%
  mutate(EV_Resource_Depletion = as.numeric(EV_Resource_Depletion)) %>% 
  count(EV_Resource_Depletion)

RD_no <- data_only_no_activity %>%
  filter(ID == id) %>%
  select(EV_Resource_Depletion)  %>%
  rowwise() %>%
  mutate(EV_Resource_Depletion = as.numeric(EV_Resource_Depletion)) %>% 
  count(EV_Resource_Depletion)

AA_free <- data_only_free_activity %>%
  filter(ID == id) %>%
  select(EV_Anger_Anxiety)  %>%
  rowwise() %>%
  mutate(EV_Anger_Anxiety = as.numeric(EV_Anger_Anxiety)) %>% 
  count(EV_Anger_Anxiety)

AA_no <- data_only_no_activity %>%
  filter(ID == id) %>%
  select(EV_Anger_Anxiety)  %>%
  rowwise() %>%
  mutate(EV_Anger_Anxiety = as.numeric(EV_Anger_Anxiety)) %>% 
  count(EV_Anger_Anxiety)

SP_free <- data_only_free_activity %>%
  filter(ID == id) %>%
  select(EV_SP_Experiences)  %>%
  rowwise() %>%
  mutate(EV_SP_Experiences = as.numeric(EV_SP_Experiences)) %>% 
  count(EV_SP_Experiences)

SP_no <- data_only_no_activity %>%
  filter(ID == id) %>%
  select(EV_SP_Experiences)  %>%
  rowwise() %>%
  mutate(EV_SP_Experiences = as.numeric(EV_SP_Experiences)) %>% 
  count(EV_SP_Experiences)

SM_free <- data_only_free_activity %>%
  filter(ID == id) %>%
  select(EV_SM_Experiences)  %>%
  rowwise() %>%
  mutate(EV_SM_Experiences = as.numeric(EV_SM_Experiences)) %>% 
  count(EV_SM_Experiences)

SM_no <- data_only_no_activity %>%
  filter(ID == id) %>%
  select(EV_SM_Experiences)  %>%
  rowwise() %>%
  mutate(EV_SM_Experiences = as.numeric(EV_SM_Experiences)) %>% 
  count(EV_SM_Experiences)

# Step 1: Add an 'Activity' column to each data frame
COG_WB_free$Activity <- "Yes"
COG_WB_no$Activity <- "No"
AFF_WB_P_free$Activity <- "Yes"
AFF_WB_P_no$Activity <- "No"
AFF_WB_N_free$Activity <- "Yes"
AFF_WB_N_no$Activity <- "No"
RD_free$Activity <- "Yes"
RD_no$Activity <- "No"
AA_free$Activity <- "Yes"
AA_no$Activity <- "No"
SP_free$Activity <- "Yes"
SP_no$Activity <- "No"
SM_free$Activity <- "Yes"
SM_no$Activity <- "No"

# Step 2: Bind rows
combined_data_WB <- bind_rows(COG_WB_free, COG_WB_no, AFF_WB_P_free, AFF_WB_P_no, AFF_WB_N_free, AFF_WB_N_no, RD_free, RD_no, AA_free, AA_no, SP_free, SP_no, SM_free, SM_no)

old_daily <- c('EV_Cognitive_Well_Being', 'EV_Affective_Well_Being_Positive', 
               'EV_Affective_Well_Being_Negative', 'EV_Resource_Depletion', 'EV_Anger_Anxiety', 'EV_SP_Experiences', 'EV_SM_Experiences')
new <- c('C_WB_AVG', 'A_WB_P_AVG', 'A_WB_N_AVG', 'RD_AVG', 'AA_AVG', 'SP_EX_AVG', 'SM_EX_AVG')

combined_data_WB <- combined_data_WB %>% rename_with(~ new, all_of(old_daily))

# Step 3: Pivot longer
combined_data_long <- combined_data_WB %>%
  pivot_longer(cols = c(C_WB_AVG, A_WB_P_AVG, A_WB_N_AVG, RD_AVG, AA_AVG, SP_EX_AVG, SM_EX_AVG),
               names_to = "variable",
               values_to = "value")

# Step 5: Filter out rows where value is NA
combined_data_long <- combined_data_long %>%
  filter(!is.na(value))

combined_data_long$Activity <- factor(combined_data_long$Activity, levels = c("No", "Yes"))
```

**Plotting satisfaction over weaks**

```{r}
selected_colors <- wes_palette("Darjeeling2")[c(2,1)]
line_colors <- wes_palette("Darjeeling2")[c(2,3)]

activity_yes_no_plot <- ggplot(combined_data_long, aes(x = value)) +
  geom_bar(aes(y = n, fill = Activity, alpha = Activity), stat = "identity", position = "identity", width = 0.5) +
  geom_density(aes(y = ..count.., color = Activity), adjust = 1) +
  facet_wrap(~ variable, scales = "free_x", switch = "x", ncol = 3) +
  labs(x = "Value", y = "Count") +
  theme_minimal() +
  theme(strip.placement = "outside",
        strip.text = element_text(face = "italic"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.text.y = element_text(size = 8),
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 7),
        legend.key.size = unit(0.3,"cm"),
        legend.position = "top",
        legend.justification='left',
        legend.box = "horizontal",
        panel.background = element_rect(fill = "grey95", color = NA),
        panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white")) +
  scale_fill_manual(values = selected_colors, guide = guide_legend(byrow = TRUE, title.position = "top", title.hjust = 0)) +
  scale_color_manual(values = line_colors) +
  scale_alpha_manual(values = c("No" = 0.5, "Yes" = 1))


print(activity_yes_no_plot)

ggsave("KDE_activity_yes_no_plot.pdf", activity_yes_no_plot, width = 16, height = 11, units = "cm")
```

------------------------------------------------------------------------

### Regression Analysis of smartphone and social media usage

**Load data**

```{r}
# Hier deinen Pfad zur Excel-Datei einfügen
excel_path = ""
data = read_excel(excel_path, sheet = "Data_scale_values", na = c("", " "))
```

**Data cleaning**

```{r}
# convert ID to factor
data$ID = as.factor(data$ID)

data$STARTED = as.POSIXct(data$STARTED) # POSIXct: contains date and time info

data$DATE = as.Date(data$DATE)
```

**Get relevant column data**

```{r}
# Hier deine ID einfügen
id = ""

# Define start and end dates
start_date <- as.Date("2024-06-24")
end_date <- as.Date("2024-07-07")

# Create logical vector indicating whether entry is within activity interval, 0 = no, 1 = yes
data$between <- ifelse(data$DATE >= start_date & data$DATE <= end_date, 1, 0)

data_only_free_activity <- data %>%
  filter(between == 1) %>%
  filter(QUESTNNR == "Daily_Evening_Survey") %>% 
  filter(EV_Activity_Check == 2)

SM_EX_own <- data_only_free_activity %>% 
  filter(ID == id) %>% 
  select(EV_SM_Experiences, DATE) %>% 
  mutate(EV_SM_Experiences = as.numeric(EV_SM_Experiences))

SM_EX_own$Group <- "Own"

SM_EX_avg <- data_only_free_activity %>% 
  filter(ID != id) %>% 
  select(EV_SM_Experiences, DATE) %>%
  group_by(DATE) %>% 
  mutate(EV_SM_Experiences = as.numeric(EV_SM_Experiences)) %>%
  summarise(EV_SM_Experiences = mean(EV_SM_Experiences, na.rm = TRUE)) %>%
  ungroup()

SM_EX_avg$Group <- "Other"

SP_EX_own <- data_only_free_activity %>% 
  filter(ID == id) %>% 
  select(EV_SP_Experiences, DATE) %>% 
  mutate(EV_SP_Experiences = as.numeric(EV_SP_Experiences))

SP_EX_own$Group <- "Own"

SP_EX_avg <- data_only_free_activity %>% 
  filter(ID != id) %>% 
  select(EV_SP_Experiences, DATE) %>%
  group_by(DATE) %>% 
  mutate(EV_SP_Experiences = as.numeric(EV_SP_Experiences)) %>% summarise(EV_SP_Experiences = mean(EV_SP_Experiences, na.rm = TRUE)) %>%
  ungroup()

SP_EX_avg$Group <- "Other"

SM_EX_comparison <- rbind(SM_EX_own, SM_EX_avg)

SP_EX_comparison <- rbind(SP_EX_own, SP_EX_avg)
```

**Plotting regression analysis of smartphone and social media usage**

```{r}
all_colors <- wes_palette("Darjeeling2")
selected_colors <- all_colors[c(1,2)]

spreed_colors <- wes_palette("Darjeeling2")[c(1)]

custom_theme <- theme_minimal() +
  theme(panel.background = element_rect(fill = "grey95", color = NA),
        panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 8, face = "bold"),
        legend.key.size = unit(0.3,"cm"),
        legend.position = "top",
        legend.justification='left',
        legend.box = "horizontal",
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 7))

guide <- guide_legend(byrow = TRUE, title.position = "top", title.hjust = 0)

# Create the SM Experiences plot
sm_plot <- ggplot(SM_EX_comparison, aes(x = DATE, y = EV_SM_Experiences, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, aes(fill = Group), formula = y ~ x) +
  labs(y = "Time on Social Media",
       color = "Data Source",
       fill = "Data Source") +
  scale_color_manual(values = selected_colors) +
  scale_fill_manual(values = c("Own" = "lightblue", "Other" = spreed_colors, guide = guide)) +
  custom_theme +
  guides(color = guide, fill = guide)

# Create the SP Experiences plot
sp_plot <- ggplot(SP_EX_comparison, aes(x = DATE, y = EV_SP_Experiences, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, aes(fill = Group), formula = y ~ x) +
  labs(y = "Time on Smartphone",
       color = "Data Source",
       fill = "Data Source") +
  scale_color_manual(values = selected_colors) +
  scale_fill_manual(values = c("Own" = "lightblue", "Other" = spreed_colors, guide = guide)) +
  custom_theme +
  guides(color = guide, fill = guide)

# Combine the plots into a 1x2 matrix
combined_plot <- sm_plot + sp_plot +
  plot_layout(ncol = 2, guides = "collect") +
  plot_annotation(title = "Comparison of Social Media and Social Presence Experiences",
                  theme = theme(plot.title = element_blank(),
                                legend.key.size = unit(0.3,"cm"),
                                legend.position = "top",
                                legend.justification='left',
                                legend.box = "horizontal")) 

print(combined_plot)

ggsave("regression_pitu_rd_plot.pdf", combined_plot, width = 16, height = 8, units = "cm")
```

------------------------------------------------------------------------

### Regression Analysis of resource deletion and social media usage

**Load data**

```{r}
# Hier deinen Pfad zur Excel-Datei einfügen
excel_path = ""
data = read_excel(excel_path, sheet = "Data_scale_values", na = c("", " "))
```

**Data cleaning**

```{r}
# convert ID to factor
data$ID = as.factor(data$ID)

data$STARTED = as.POSIXct(data$STARTED) # POSIXct: contains date and time info

data$DATE = as.Date(data$DATE)
```

**Get relevant column data**

```{r}
# Hier deine ID einfügen
id = ""

# Define start and end dates
start_date <- as.Date("2024-06-24")
end_date <- as.Date("2024-07-07")

# Create logical vector indicating whether entry is within activity interval, 0 = no, 1 = yes
data$between <- ifelse(data$DATE >= start_date & data$DATE <= end_date, 1, 0)

data_only_free_activity <- data %>%
  filter(between == 1) %>%
  filter(QUESTNNR == "Daily_Evening_Survey") %>% 
  filter(EV_Activity_Check == 2)


PITU_EX_own <- data_only_free_activity %>% 
  filter(QUESTNNR == "Daily_Evening_Survey") %>% 
  filter(ID == id) %>% 
  select(EV_PITU_Experiences, DATE) %>% 
  mutate(EV_PITU_Experiences = as.numeric(EV_PITU_Experiences))

PITU_EX_own $Group <- "Own"

PITU_EX_other_avg <- data_only_free_activity %>% 
  filter(ID != id) %>% 
  select(EV_PITU_Experiences, DATE) %>%
  group_by(DATE) %>% 
  mutate(EV_PITU_Experiences = as.numeric(EV_PITU_Experiences)) %>%
  summarise(EV_PITU_Experiences = mean(EV_PITU_Experiences, na.rm = TRUE)) %>%
  ungroup()

PITU_EX_other_avg $Group <- "Other"

RD_own <- data_only_free_activity %>% 
  filter(ID == id) %>% 
  select(EV_Resource_Depletion, DATE) %>% 
  mutate(EV_Resource_Depletion = as.numeric(EV_Resource_Depletion))

RD_own$Group <- "Own"

RD_other_avg <- data_only_free_activity %>% 
  filter(ID != id) %>% 
  select(EV_Resource_Depletion, DATE) %>%
  group_by(DATE) %>% 
  mutate(EV_Resource_Depletion = as.numeric(EV_Resource_Depletion)) %>%
  summarise(EV_Resource_Depletion = mean(EV_Resource_Depletion, na.rm = TRUE)) %>%
  ungroup()

RD_other_avg$Group <- "Other"


PITU_EX_comparison <- rbind(PITU_EX_own, PITU_EX_other_avg )

RD_comparison <- rbind(RD_own, RD_other_avg)
```

**Plotting regression analysis of resource deletion and social media usage**

```{r}
all_colors <- wes_palette("Darjeeling2")
selected_colors <- all_colors[c(1,2)]

spreed_colors <- wes_palette("Darjeeling2")[c(1)]

custom_theme <- theme_minimal() +
  theme(panel.background = element_rect(fill = "grey95", color = NA),
        panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 8, face = "bold"),
        legend.key.size = unit(0.3,"cm"),
        legend.position = "top",
        legend.justification='left',
        legend.box = "horizontal",
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 7))

guide <- guide_legend(byrow = TRUE, title.position = "top", title.hjust = 0)

# Create the PITU plot
pitu_plot <- ggplot(PITU_EX_comparison, aes(x = DATE, y = EV_PITU_Experiences, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, aes(fill = Group), formula = y ~ x) +
  labs(y = "Time on IT",
       color = "Data Source",
       fill = "Data Source") +
  scale_color_manual(values = selected_colors) +
  scale_fill_manual(values = c("Own" = "lightblue", "Other" = spreed_colors, guide = guide)) +
  custom_theme +
  guides(color = guide, fill = guide)

# Create the RD plot
rd_plot <- ggplot(RD_comparison, aes(x = DATE, y = EV_Resource_Depletion, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE, aes(fill = Group), formula = y ~ x) +
  labs(y = "Degree of Resource Depletion",
       color = "Data Source",
       fill = "Data Source") +
  scale_color_manual(values = selected_colors) +
  scale_fill_manual(values = c("Own" = "lightblue", "Other" = spreed_colors, guide = guide)) +
  custom_theme +
  guides(color = guide, fill = guide)

# Combine the plots into a 1x2 matrix
combined_plot <- pitu_plot + rd_plot +
  plot_layout(ncol = 2, guides = "collect") +
  plot_annotation(title = "",
                  theme = theme(plot.title = element_blank(),
                                legend.key.size = unit(0.3,"cm"),
                                legend.position = "top",
                                legend.justification='left',
                                legend.box = "horizontal")) 

print(combined_plot)

ggsave("regression_sp_sm_plot.pdf", combined_plot, width = 16, height = 8, units = "cm")
```

------------------------------------------------------------------------

------------------------------------------------------------------------

## Analyse objective data

### Plot active time per week

**Load data**

```{r}
# Hier deinen Pfad zur Excel-Datei einfügen
excel_path = ""
data = read_excel(excel_path, sheet = "Data_active_time", na = c("", " "))
```

**Data cleaning**

```{r}
data$DATE = as.Date(data$DATE)
```

**Get relevant data**

```{r}
# Define start and end dates
start_date <- as.Date("2024-06-24")
end_date <- as.Date("2024-07-07")

# Create logical vector indicating whether entry is within activity interval, 0 = no, 1 = yes
data$between <- ifelse(data$DATE >= start_date & data$DATE <= end_date, 1, 0)

data_activity <- data %>%
  filter(!is.na(WEEK)) %>%
  filter(between == 1) %>%
  select(DATE, WEEK, EV_Active_Time) %>%
  group_by(WEEK) %>%
  summarize(Total_Active_Time = sum(EV_Active_Time, na.rm = TRUE))

data_activity_date <- data %>%
  filter(between == 1) %>% 
  filter(!is.na(DATE), !is.na(EV_Active_Time)) %>%
  select(DATE, EV_Active_Time)
```

**Plotting active time per week**

```{r}
selected_colors <- brewer.pal(9, "Blues")[c(4, 5, 6)]
line_color <- wes_palette("Darjeeling2")[c(2)]
dotted_line_color <- wes_palette("Darjeeling2")[c(3)]

custom_theme <- theme_minimal() +
  theme(panel.background = element_rect(fill = "grey95", color = NA),
        panel.grid.major = element_line(color = "white"),
        panel.grid.minor = element_line(color = "white"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 8, face = "bold"),
        legend.key.size = unit(0.3,"cm"),
        legend.position = "top",
        legend.justification='left',
        legend.box = "horizontal",
        legend.title = element_text(size = 8, face = "bold"),
        legend.text = element_text(size = 7))

active_time_plot <- ggplot(data_activity, aes(x = WEEK, y = Total_Active_Time)) +
  geom_bar(stat = "identity", fill = selected_colors) +
  labs(title = "Total Active Time per Week", x = "Week", y = "Minutes") +
  custom_theme +
  theme(title = element_text(size = 9, face = "bold"))

active_time_over_days_plot <- ggplot(data_activity_date, aes(x = DATE, y = EV_Active_Time)) +
  geom_line(aes(color = "Active Time"), size = 0.8) +
  geom_point(aes(color = "Active Time"), size = 1.1) +
  geom_hline(aes(yintercept = 30, linetype = "Daily Goal"), color = dotted_line_color, size = 0.8) + 
  scale_color_manual(name = "Legend", values = c("Active Time" = line_color)) +
  scale_linetype_manual(name = "Legend", values = c("Daily Goal" = "dashed")) +
  labs(title = "Active Time per Day", x = "Day", y = "Minutes") +
  custom_theme +
  theme(title = element_text(size = 9, face = "bold"),
        legend.title = element_blank(),
        legend.position = "top",
        legend.justification = 'left',
        legend.box = "horizontal",
        legend.key.size = unit(0.3,"cm"),
        legend.text = element_text(size = 8)) +
  scale_y_continuous(breaks = function(x) c(unique(floor(pretty(x))), 30)) +
  scale_x_date(date_labels = "%b %d", date_breaks = "2 day", limits = c(start_date, end_date))

combined_plot <- active_time_plot + active_time_over_days_plot +
  plot_layout(ncol = 1, heights = c(1, 1)) +
  plot_annotation(theme = theme(plot.title = element_blank()))

print(combined_plot)

ggsave("movement_time_per_week_plot.pdf", combined_plot, width = 16, height = 11, units = "cm")
```
